Supplementary Material for the article \textit{Quotient Normalized Maximum Likelihood Criterion for Learning Bayesian Network Structures}

### 2017-10-13 qnml.tex
added a reference for BDq

>>>>

Suzuki \cite{Suzuki2017} independently introduces a Bayesian Dirichlet
quotient (BDq) score, that can also be shown to be score equivalent
and regular.  However, like BDeu, this score features a single
hyperparameter $\alpha$, and our initial studies suggest that BDq is
also very sensitive to this hyperparameter (see Appendix D in the
Supplementarty Material), the issue that was one of the main
motivations to develop a parameter-free model selection criterion like
qNML.
